---
title: "The `genind` object cheat sheet"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

___

__Note:__ We will use `myData` to refer to the `genind` object.

___


## Basic Info

You can view basic information about data in a `genind` file:

- number of biological samples (called individuals): `nInd(myData)`

- number of loci: `nLoc(myData)`

- number of pops: `nPop(myData)`

- locus names: `locNames(myData)`

- alleles by locus: `alleles(myData)`

- biological sample names: `indNames(myData)`

- population names: `popNames(myData)`

- pop-ID for each sample: `pop(myData)`


___

## Rename loci

Create a vector with locus names.

```{r, eval=FALSE}
newLocNames <- c("locus-1","locus-2","locus-3") ## define as many names as loci!
```

Then re-name loci in `genind` object.

```{r, eval=FALSE}
locNames(myData) <- newLocNames
```

___


## Rename populations

Create a vector with locus names.

```{r, eval=FALSE}
newPopNames <- c("pop-1","pop-2","pop-3") ## define as many names as populations!
```

Then re-name loci in `genind` object.

```{r, eval=FALSE}
popNames(myData) <- newPopNames
```


___

## Remove individuals

Create a vector of individuals to remove.

```{r, eval=FALSE}
removeInd <- c("ind-1", "ind-2", "ind-3")
```

Then remove from `genind` object.

```{r, eval=FALSE}
myData <- myData[!row.names(myData@tab) %in% removeInd]
```

___

## Remove loci

```{r, eval=FALSE}
removeLoci <- c("locus-1","locus-2","locus-3")
myData <- myData[loc = !locNames(myData) %in% removeLoci, drop = TRUE]
```


__Note:__ if you know the element ID of the loci to be removed, can use the following (in this example, loci 1 & 2)

```{r, eval=FALSE}
myData <- myData[loc = -c(1,2), drop = TRUE]
```

___

## Remove populations

```{r, eval=FALSE}
removePop <- c("pop-1","pop-2")
myData <- myData[pop = !popNames(myData) %in% removePop]
```

__Note:__ if you know the element ID of the populations to be removed, can use the following (in this example, populations 1 & 2)

```{r, eval=FALSE}
myData <- myData[pop = -c(1,2)]
```

___

# The `seppop()` function

This function splits a `genind` object into a list, with each element of the list consisting of a `genind` object for a single population.

This enables iteration through the dataset by population. E.g. by using `lapply()`.

___

# The `summary()` function

This function provides the following information:

- Number of individuals
- Group sizes
- Number of alleles per locus
- Number of alleles per group
- Percentage of missing data
- Observed heterozygosity
- Expected heterozygosity

This information can also be called. E.g. for expected heterozygosity:

```{r, eval=FALSE}
summary(myData)$Hexp
```




